Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-04 article.tex
Rerun on Macbook Air M2

To evaluate SimBio's performance,
we selected \ac{SBML} models from the curated section of BioModels \cite{malik-sheriffBioModels15Years2020}.
Among the first 250 models,
we considered the 117 that used supported \ac{SBML} features.
We ran simulations
on a MacBook Pro with M2 Pro CPU
using
COPASI v4.42.284
(with BasiCO v0.64) with the LSODA solver,
RoadRunner v2.5.0 (with Tellurium v2.2.10) with the comparable CVODE solver, and
SimBio v0.3.2 with the LSODA solver.
For SimBio, we considered three variants:
NumPy (v1.26.4) backend and scipy (v1.12)'s LSODA solver,
Numba (v0.59.0) backend and scipy's LSODA solver,
Numba backend and numbalsoda's LSODA solver.
In all cases, we used a relative tolerance of \(10^{-6}\) and absolute tolerances of \(10^{-9}\).
We measured two simulation stages:
an initial cold run that includes the reading of the \ac{SBML} model
and subsequent warm runs.

>>>>

To evaluate SimBio's performance,
we selected \ac{SBML} models from the curated section of BioModels \cite{malik-sheriffBioModels15Years2020}.
Among the first 250 models,
we considered the 117 that used supported \ac{SBML} features.
We ran simulations
on a MacBook Air with M2 CPU
using Python 3.11.8,
COPASI v4.42.284
(with BasiCO v0.58) with the LSODA solver,
RoadRunner v2.5.0 (with Tellurium v2.2.10) with the comparable CVODE solver, and
SimBio v0.3.2 with the LSODA solver.
For SimBio, we considered three variants:
NumPy (v1.26.4) backend and scipy (v1.12.0)'s LSODA solver,
Numba (v0.59.0) backend and scipy's LSODA solver,
Numba backend and numbalsoda's (v0.3.5) LSODA solver.
In all cases, we used a relative tolerance of \(10^{-6}\) and absolute tolerances of \(10^{-9}\).
We measured two simulation stages:
an initial cold run that includes the reading of the \ac{SBML} model
and subsequent warm runs.
